### 2015-06-17 paper/review-progress.Rmd
adds some DONE's to to-do list

>>>>

### TODO

- Drop a plot or two (dropped shortages plot) DONE
- Make circles same size in dotplots (DONE), add error bars 
- Add histograms as subplots to facets for time spent studying (Not possible, se bands have been added) DONE
- paragraph on fishing (Di) DONE
- Clean language on middle east surprise DONE
- Age started vs years in school (DON'T PLAN TO DO ANYTHING ON THIS)

### My email to Brian Tarran
